Stability in human interaction networks: primitive typology of vertex, prominence of measures and activity statistics

### 2015-01-20 paper.tex
terminada revisao completa do artigo

\begin{table}
  \centering
  \begin{tabular}{|l|c|c|c|c|c|}\hline
list & $date_1$ & $date_{M}$    & $N$  & $\Gamma$ & $\overline{M}$ \\\hline
LAU  & Jun/29/2003 & Jul/23/2005 & 1183 & 3373 & 5 \\
LAD  & Jun/30/2003 & Oct/07/2009 & 1268 & 3113 & 4 \\
MET  & Ago/01/2005 & Mar/07/2008 & 492  & 4607 & 23 \\
CPP  & Mar/13/2002 & Aug/25/2009 & 1052 & 4506 & 7 \\ \hline
  \end{tabular}
  \caption{Columns $date_1$ and $date_M$ have first and last messages dates from the 20,000 messages considered.
$N$ is the number of participants (number of different email addresses).
$\Gamma$ is the number of threads (count of messages without antecedent).
$\overline{M}$ is messages missing in the 20,000 collection, $100\frac{23}{20000}=0.115$ percent in the worst case.
MET notably has the fewer participants and the larger number of threads.
This relation holds for each pair of the lists considered: as the number of participants increases,
 the number of threads decreases.}
  \label{geralListas}
\end{table}

@@

\begin{figure}[hb]
    \centering
    \includegraphics[width=0.5\textwidth]{figs/criaRede_}
    \caption{Formation of interaction network from email messages. Each vertex represents a participant. If participant B replies participant A, that is regarded as evidence that B received information from A. Multiple messages add ``weight'' to directed edge. Further details are in Section~\ref{intNet}.}
    \label{formationNetwork}
\end{figure}

@@

\begin{figure}[hb]
    \centering
    \includegraphics[width=0.5\textwidth]{figs/fser}
    \caption{Degree distribution on scale-free and Erd\"os-R\'enyi ideal networks. The later has more
        intermediary, as the former has more peripheral and hub vertexes. Sections are
        given by the two intersections of the distributions $k_1$ and $k_2$. Characteristic degrees
    are in compact intervals of degree: $[0,k_1]$, $(k_1,k_2]$, $(k_2,k_{max}]$ for the three sections considered (periphery, intermediary and hubs).}
    \label{fig:setores}
\end{figure}

@@

Classification criteria exposed in Section~\ref{sectioning} was used efficiently with windows of at least 200 messages. Specially with 1000 or more messages, criteria yields stable fractions of $\approx 5\%$ of hubs, $\approx [15-20]\%$ of intermediary and $\approx [75-80]\%$ peripheral vertex, which match literature~\cite{priSect}. A compound criteria, also described in Section~\ref{sectioning}, can be used as a classification refinement. This is specially useful in dealing with fewer messages, in which case the structure degenerates with respect to some of the degree and strength measures, but not all.
A minimum window size for observation of more general properties can be inferred by monitoring the giant component and the degeneration of hub, intermediary and peripheral sections. This degeneration is critical in the span of 50-100 messages for window sizes. With compound criteria, such as exclusive cascade of Figure~\ref{fig:cpp250_}, the networks seem to hold basic structure even with as few as 20-50 messages. This indicates that concentration of activity and low-activity participants occurs even with very few messages.

@@

\begin{figure} 
   \centering
        \includegraphics[width=\columnwidth]{figs/ev0pr11CC}
    \caption{Clustering versus degree of vertex in interaction network observed, $ws = 1000$ email messages, LAU list. General layout is in accordance with literature: connected vertexes have low clusterization while higher clusterization is gradually more incident as number of connections is lowered.}
    \label{clust}
\end{figure}

@@

This work aimed at finding common characteristics among (email) interaction networks. Analysis involved primary measures observance and formal criteria for coherent ratios of hub, intermediary and hub sectors. Nevertheless, inspection done by visualizations and raw data manipulations suggests agents peculiarities of typological character. These are initial observations, which should be further developed as posed in Section~\ref{sec:ftyp}:

@@

A related work observed textual production of network sectors~\cite{textProd}. Resulting knowledge purposes networks and participants tipologization, and both topological and textual analysis should foster characterization of interaction networks and participation incidences in a dedicated study.
Stability reported in this article eases tipologization of outliers and more usual participation patterns.

@@

Field ``In-Reply-To'' has only the ID of the message it replies and can be sometimes
a shortcut or an alternative to ``References''. Also, the textual content of the messages,
accessed through ``payload'' method of the mbox message object, is of central interest and
the authors dedicated an article to include the textual content of the messages to the analysis~\cite{textProd}.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{|l|c|c| c|c| c|c|}\hline
 & \multicolumn{2}{c|}{PC1}          & \multicolumn{2}{c|}{PC2} & \multicolumn{2}{c|}{PC3}  \\\hline
       & $\mu$            & $\sigma$ & $\mu$         & $\sigma$ & $\mu$ & $\sigma$  \\\hline
$d$       & {\bf 48.02}   & 1.39     & 2.82          & 1.74     & 48.09  & 0.32 \\
$cc$      & 4.12          & 2.94     & {\bf 90.45}   & 3.98     & 3.98  & 0.77 \\ 
$bt$      & {\bf 47.87}   & 1.55     & 6.74          & 4.08     & 47.93 & 0.46 \\ \hline
$\lambda$ & 64.67         & 0.52     & 33.26         & 0.23     & 2.08  & 0.40 \\ \hline
  \end{tabular}
  \caption{Principal components composition in the simplest case: with degree, clustering coefficient and betweenness centrality. LAU list, $ws=1000$ messages in 20 disjoint positioning was used for statistics. First component is a pondered sum of degree and betweenness centrality measures. Second component is mostly clustering coefficient. First and second components sum more than 95\% of total dispersion.}
  \label{compPCA0}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|l|c|c| c|c| c|c|}\hline
 & \multicolumn{2}{c|}{PC1} & \multicolumn{2}{c|}{PC2} & \multicolumn{2}{c|}{PC3}  \\\hline
       & $\mu$ & $\sigma$ & $\mu$ & $\sigma$ & $\mu$ & $\sigma$  \\\hline
$d$       & {\bf 14.58} & 0.14 & 0.43  & 0.35 & 1.51  & 1.08 \\
$d^{in}$  & {\bf 14.12} & 0.14 & 1.71  & 1.22 & 17.80 & 6.20 \\
$d^{out}$ & {\bf 13.95} & 0.12 & 2.80  & 1.83 & 21.15 & 5.62 \\
$s$       & {\bf 14.48} & 0.13 & 0.78  & 0.65 & 5.51  & 4.71 \\ 
$s^{in}$  & {\bf 14.10} & 0.14 & 2.17  & 1.28 & 17.32 & 6.11 \\ 
$s^{out}$ & {\bf 14.05} & 0.13 & 2.08  & 1.14 & 19.31 & 4.86 \\ \hline
$cc$      & 0.99        & 0.70 & {\bf 83.38} & 4.83 & 2.75  & 1.62 \\ 
$bt$      & {\bf 13.73} & 0.19 & 6.65  & 1.31 & 14.66 & 10.14 \\ \hline
$\lambda$ & 81.80 & 0.83 & 12.53 & 0.09  & 3.24 & 0.62 \\ \hline
  \end{tabular}
  \caption{Principal components' composition in percentages. LAU list, $ws=1000$ messages in 20 disjoint positioning was used for statistics. First component is a pondered sum of degree and strength measures and betweenness centrality. Second component is mostly clustering coefficient. First and second components sum more than 90\% of dispersion.}
  \label{compPCA}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|l|c|c| c|c| c|c|}\hline
 & \multicolumn{2}{c|}{PC1} & \multicolumn{2}{c|}{PC2} & \multicolumn{2}{c|}{PC3}  \\\hline
       & $\mu$ & $\sigma$ & $\mu$ & $\sigma$ & $\mu$ & $\sigma$  \\\hline
$d$            & {\bf 11.51} & 0.42 & 2.00  & 0.76 & 2.39  & 0.49 \\ 
$d^{in}$       & {\bf 11.45} & 0.34 & 2.86  & 0.91 & 1.68  & 0.67 \\
$d^{out}$      & {\bf 10.68} & 0.60 & {\bf 7.43}  & 1.00 & 3.00  & 1.02 \\
$s$            & {\bf 11.37} & 0.42 & 1.75  & 0.71 & 4.31  & 0.63 \\ 
$s^{in}$       & {\bf 11.33} & 0.35 & 2.39  & 1.10 & 3.69  & 0.86 \\ 
$s^{out}$      & {\bf 10.74} & 0.55 & {\bf 6.14}  & 1.05 & 4.75  & 0.98 \\ \hline
$cc$           & 0.91        & 0.64 & 2.68  & 1.67 & {\bf 22.27} & 6.43 \\ 
$bt$           & {\bf 10.87} & 0.38 & 1.17  & 0.93 & 4.03  & 1.42 \\ \hline
$asy$          & 3.99        & 1.45 & {\bf 18.13} & 1.67 & 2.55  & 1.77 \\
$\mu_{asy}$    & 4.15        & 1.40 & {\bf 17.07} & 1.78 & 2.49  & 1.67 \\
$\sigma_{asy}$ & 1.21        & 0.67 & {\bf 17.49} & 0.79 & 3.29  & 2.33 \\
$dis$          & 5.78        & 0.51 & 1.94  & 1.28 & {\bf 24.75} & 3.73 \\
$\mu_{dis}$    & 0.79        & 0.49 & {\bf 14.00} & 1.14 & 3.73  & 3.13 \\
$\sigma_{dis}$ & 5.18        & 0.72 & 4.93  & 2.48 & {\bf 17.04} & 4.78 \\ \hline
$\lambda$      & 51.09       & 1.07 & 20.04 & 1.31 & 9.23  & 6.63 \\ \hline
  \end{tabular}
  \caption{Distribution of components, added measures of symmetry described in subsection~\ref{measures}. LAU list, $ws=1000$ messages in 20 disjoint positioning was used for statistics. In this case, clusterization is pushed to third component, with disequilibrium measures. Second component is primarily symmetry measures, but also some out degree and strength contribution. Betweenness again has a role similar to degree, but weaker. Clusterization component combines with disequilibrium, while asymmetry is related to out degree and strength. Three components has in average 80.36\% of dispersion.}
  \label{compPCA2}
\end{table}

@@

\subsection{Tables for activity along time}\label{tabTime}
\begin{table*}
%\tiny
    \caption{Hours of the day and percentage of activity ($\frac{\text{counted messages}}{\text{total messages}}$) in each hour, 6 hours and 12 hours. Maximum activity rates are in bold. In hour columns, minimum activity is also bold. The less active period of the day is around 4-6h. Maximum activity is between 10-13h. Afternoon is most active in 6h division of the day. The noon has $\approx \frac{2}{3}$ of 24h activity. }
\begin{center}
    \begin{tabular}{ |l|| c|c|c| c|c|c| c|c|c| c|c|c|}
        \hline
    & \multicolumn{3}{c|}{CPP} & \multicolumn{3}{c|}{MET} & \multicolumn{3}{c|}{LAU} & \multicolumn{3}{c|}{LAD}  \\ \hline
    & 1h   & 6h & 12h &   1h & 6h & 12h &   1h & 6h & 12h &   1h & 6h & 12h \\ \hline\hline
0h  & 3.66 & \multirow{6}{*}{10.67} & \multirow{12}{*}{33.76} & 2.87  & \multirow{6}{*}{7.15} & \multirow{12}{*}{29.33} & 3.58 & \multirow{6}{*}{10.14} &  \multirow{12}{*}{36.88} & 4.00 & \multirow{6}{*}{10.77} & \multirow{12}{*}{33.13} \\
1h  & 2.76 &                        &                         & 1.77  & & &  2.22 & & & 2.52 & & \\
2h  & 1.79 &                        &                         & 1.04  & & & 1.63 & & & 1.79 & & \\
3h  & 1.10 &                        &                         & 0.64  & & & 1.06 & & & 1.06 & & \\
4h  & {\bf 0.68} &                        &                         & 0.47  & & &  0.84 & & & 0.75 & & \\
5h  & 0.69 &                        &                         & {\bf 0.38}  & & & {\bf 0.82} & & & {\bf 0.66} & & \\\cline{3-3}\cline{6-6}\cline{9-9}\cline{12-12}
6h  & 0.83 & \multirow{6}{*}{23.09} &                         & 0.72  & \multirow{6}{*}{22.18} & & 1.17 & \multirow{6}{*}{26.74} & & 0.85 & \multirow{6}{*}{22.36} &  \\
7h  & 1.24 &                        &                         & 1.33  & & & 2.37 & & & 1.56 & & \\
8h  & 2.28 &                        &                         & 2.67  & & & 3.54 & & & 2.96 & & \\
9h  & 4.52 &                        &                         & 4.40  & & & 6.04 & & & 4.68 & & \\
10h & 6.62 &                        &                         & 6.29  & & & {\bf 6.83} & & & 5.93 & & \\
11h & {\bf 7.61} &                        &                         & 6.78  & & & 6.79 & & & 6.40 & & \\\hline
12h & 6.44 & \multirow{6}{*}{\bf 37.63} & \multirow{12}{*}{\bf 66.24} & {\bf 7.33}  & \multirow{6}{*}{\bf 42.22} & \multirow{12}{*}{ \bf 70.66} & 6.11 & \multirow{6}{*}{\bf 35.65} &  \multirow{12}{*}{ \bf 63.12} & {\bf 6.41} & \multirow{6}{*}{\bf 37.25} &  \multirow{12}{*}{\bf 66.87} \\
13h & 6.04 &                        &                         & 7.08  & & & 6.26 & & & 6.12 & & \\
14h & 6.47 &                        &                         & 7.09  & & & 6.38 & & & 6.33 & & \\
15h & 6.10 &                        &                         & 7.14  & & & 5.93 & & & 5.98 & & \\
16h & 6.22 &                        &                         & 6.68  & & & 5.52 & & & 6.40 & & \\
17h & 6.36 &                        &                         & 6.89  & & & 5.46 & & & 6.02 & & \\\cline{3-3}\cline{6-6}\cline{9-9}\cline{12-12}

@@

\begin{table*}
%\tiny
    \caption{Activity along the days of the month. As can be noted, the pattern is to have no clear prevalent period. One might point a slight tendency for the first two weeks to be more active, although this table does not present statistical foundation for such an assumption. For the scope of this study, differences of activity along the month is assumed to be non existent.}
\begin{center}
    \begin{tabular}{ |l|| c|c|c| c|c|c| c|c|c| c|c|c|}
        \hline
    & \multicolumn{3}{c|}{CPP} & \multicolumn{3}{c|}{MET} & \multicolumn{3}{c|}{LAU} & \multicolumn{3}{c|}{LAD}  \\ \hline
day    & 1 day & 7 days & 14 days &   1 day & 7 days & 14 days &   1 day & 7 days & 14 days &   1 day & 7 days & 14 days \\ \hline\hline
1  & 3.19 & \multirow{7}{*}{23.05} & \multirow{14}{*}{45.63} & 3.01 & \multirow{7}{*}{25.16} & \multirow{14}{*}{48.08} & 3.34 & \multirow{7}{*}{23.06} &  \multirow{14}{*}{47.31} & 3.22 & \multirow{7}{*}{21.96} & \multirow{14}{*}{46.70} \\
2  & 3.07 &                        &                         & 3.38  & & &  3.38 & & & 3.42 & & \\
3  & 3.20 &                        &                         & 3.55  & & & 3.20 & & & 2.87 & & \\
4  & 3.63 &                        &                         & 4.34  & & & 3.52 & & & 2.91 & & \\
5  & 2.85 &                        &                         & 3.93  & & &  2.68 & & & 3.30 & & \\
6  & 3.67 &                        &                         & 3.76  & & & 3.18 & & & 3.52 & & \\
7  & 3.45 &                        &                         & 3.18  & & & 3.77 & & & 2.27 & & \\\cline{3-3}\cline{6-6}\cline{9-9}\cline{12-12}
8  & 3.12 & \multirow{7}{*}{22.57} &                         & 3.36  & \multirow{7}{*}{22.92} & & 3.62 & \multirow{7}{*}{24.25} & & 3.72 & \multirow{7}{*}{24.73} &  \\
9  & 2.57 &                        &                         & 3.44  & & & 3.82 & & & 3.97 & & \\
10  & 2.92 &                        &                         & 3.17  & & & 3.06 & & & 3.77 & & \\
11  & 3.54 &                        &                         & 3.88  & & & 3.11 & & & 3.27 & & \\
12 & 3.23 &                        &                         & 2.94  & & & 3.40 & & & 2.75 & & \\
13 & 3.39 &                        &                         & 3.29  & & & 3.55 & & & 3.34 & & \\
14 & 3.81 &                        &                         & 2.83  & & & 3.69 & & & 3.93 & & \\\hline
15 & 3.35 & \multirow{7}{*}{23.02} & \multirow{14}{*}{46.31} & 2.72  & \multirow{7}{*}{21.87} & \multirow{14}{*}{ 43.56} & 3.23 & \multirow{7}{*}{22.84} &  \multirow{14}{*}{ 44.01 } & 3.37 & \multirow{7}{*}{22.82} &  \multirow{14}{*}{46.00} \\
16 & 3.77 &                        &                         & 2.96  & & & 2.94 & & & 3.37 & & \\
17 & 3.45 &                        &                         & 3.01  & & & 3.02 & & & 2.95 & & \\
18 & 3.47 &                        &                         & 3.39  & & & 3.63 & & & 3.22 & & \\
19 & 2.90 &                        &                         & 3.42  & & & 3.16 & & & 3.59 & & \\
20 & 2.80 &                        &                         & 3.09  & & & 3.25 & & & 3.21 & & \\
21 & 3.29 &                        &                         & 3.27  & & & 3.61 & & & 3.13 & & \\\cline{3-3}\cline{6-6}\cline{9-9}\cline{12-12}

>>>>

\begin{table}
  \centering
  \caption{Columns $date_1$ and $date_M$ have first and last message dates from the 20,000 messages considered in each email list.
$N$ is the number of participants (number of different email addresses).
$\Gamma$ is the number of threads (count of messages without antecedent).
$\overline{M}$ is messages missing in the 20,000 collection, $100\frac{23}{20000}=0.115$ percent in the worst case.
MET notably has the fewer participants and the larger number of threads.
This relation holds for each pair of the lists considered: as the number of participants increases,
 the number of threads decreases.}
  \label{geralListas}
  \begin{tabular}{|l|c|c|c|c|c|}\hline
list & $date_1$ & $date_{M}$    & $N$  & $\Gamma$ & $\overline{M}$ \\\hline
LAU  & Jun/29/2003 & Jul/23/2005 & 1183 & 3373 & 5 \\
LAD  & Jun/30/2003 & Oct/07/2009 & 1268 & 3113 & 4 \\
MET  & Ago/01/2005 & Mar/07/2008 & 492  & 4607 & 23 \\
CPP  & Mar/13/2002 & Aug/25/2009 & 1052 & 4506 & 7 \\ \hline
  \end{tabular}
\end{table}

@@

\begin{figure}[hb]
    \centering
    \includegraphics[width=0.5\textwidth]{figs/criaRede_}
    \caption{Formation of interaction network from email messages. Each vertex represents a participant. A reply message from participant B to a message from participant A is considered as evidence that B received information from A. Multiple messages add ``weight'' to directed edge. Further details are in Section~\ref{intNet}.}
    \label{formationNetwork}
\end{figure}

@@

\begin{figure}[hb]
    \centering
    \includegraphics[width=0.5\textwidth]{figs/fser}
    \caption{Degree distribution on scale-free and Erd\"os-R\'enyi ideal networks. The later has more
        intermediary, as the former has more peripheral and hub vertexes. Sections are
        given by the two intersections $k_1$ and $k_2$ of the connectivity distributions. Characteristic degrees
    are in compact intervals of degree: $[0,k_1]$, $(k_1,k_2]$, $(k_2,k_{max}]$ for the three sections considered (periphery, intermediary and hubs).}
    \label{fig:setores}
\end{figure}

@@

Classification criteria exposed in Section~\ref{sectioning} was used efficiently with windows of at least 200 messages. Specially with 1000 or more messages, criteria yields stable fractions of $\approx 5\%$ of hubs, $\approx [15-20]\%$ of intermediary and $\approx [75-80]\%$ peripheral vertex, which match literature expectations~\cite{secFree}. A compound criteria, also described in Section~\ref{sectioning}, can be used as a classification refinement. This is specially useful in dealing with fewer messages, in which case the structure degenerates with respect to some of the degree and strength measures, but not all.
A minimum window size for observation of more general properties can be inferred by monitoring the giant component and the degeneration of hub, intermediary and peripheral sections. This degeneration is critical in the span of 50-100 messages for window sizes. With compound criteria, such as exclusive cascade of Figure~\ref{fig:cpp250_}, the networks seem to hold basic structure even with as few as 20-50 messages. This indicates that concentration of activity and low-activity participants occurs even with very few messages.

@@

\begin{figure} 
   \centering
        \includegraphics[width=\columnwidth]{figs/ev0pr11CC}
    \caption{Clustering versus degree of vertex with a window size of $ws = 1000$ email messages (LAU list). General layout is in accordance with literature: connected vertexes have low clusterization while higher clusterization is gradually more incident as number of connections is lowered.}
    \label{clust}
\end{figure}

@@

This work aimed at finding common characteristics among (email) interaction networks. Analysis involved primary measures observance and formal criteria for coherent ratios of hub, intermediary and hub sectors. Nevertheless, inspection done by visualizations and raw data manipulations suggests agents peculiarities of typological character. These are initial observations, which should be further developed as posed in Section~\ref{constDisc}:

@@

A related work observed textual production of network sectors~\cite{rcText}. Resulting knowledge purposes networks and participants tipologization, and both topological and textual analysis should foster characterization of interaction networks and participation incidences in a dedicated study.
Stability reported in this article eases tipologization of outliers and more usual participation patterns.

@@

Field ``In-Reply-To'' has only the ID of the message it replies and can be sometimes
a shortcut or an alternative to ``References''. Also, the textual content of the messages,
accessed through ``payload'' method of the mbox message object, is of central interest and
the authors dedicated an article to include the textual content of the messages to the analysis~\cite{rcText}.

@@

\begin{table}[H]
  \centering
  \caption{Principal components composition in the simplest case: with degree, clustering coefficient and betweenness centrality. LAU list, $ws=1000$ messages in 20 disjoint positioning was used for statistics. First component is a pondered sum of degree and betweenness centrality measures. Second component is mostly clustering coefficient. First and second components sum more than 95\% of total dispersion.}
  \begin{tabular}{|l|c|c| c|c| c|c|}\hline
 & \multicolumn{2}{c|}{PC1}          & \multicolumn{2}{c|}{PC2} & \multicolumn{2}{c|}{PC3}  \\\hline
       & $\mu$            & $\sigma$ & $\mu$         & $\sigma$ & $\mu$ & $\sigma$  \\\hline
$d$       & {\bf 48.02}   & 1.39     & 2.82          & 1.74     & 48.09  & 0.32 \\
$cc$      & 4.12          & 2.94     & {\bf 90.45}   & 3.98     & 3.98  & 0.77 \\ 
$bt$      & {\bf 47.87}   & 1.55     & 6.74          & 4.08     & 47.93 & 0.46 \\ \hline
$\lambda$ & 64.67         & 0.52     & 33.26         & 0.23     & 2.08  & 0.40 \\ \hline
  \end{tabular}
  \label{compPCA0}
\end{table}

\begin{table}
  \centering
  \caption{Principal components composition in percentages. LAU list, $ws=1000$ messages in 20 disjoint positioning was used for statistics. First component is a pondered sum of degree and strength and betweenness centrality measures. Second component is mostly clustering coefficient. First and second components sum more than 90\% of dispersion.}
  \begin{tabular}{|l|c|c| c|c| c|c|}\hline
 & \multicolumn{2}{c|}{PC1} & \multicolumn{2}{c|}{PC2} & \multicolumn{2}{c|}{PC3}  \\\hline
       & $\mu$ & $\sigma$ & $\mu$ & $\sigma$ & $\mu$ & $\sigma$  \\\hline
$d$       & {\bf 14.58} & 0.14 & 0.43  & 0.35 & 1.51  & 1.08 \\
$d^{in}$  & {\bf 14.12} & 0.14 & 1.71  & 1.22 & 17.80 & 6.20 \\
$d^{out}$ & {\bf 13.95} & 0.12 & 2.80  & 1.83 & 21.15 & 5.62 \\
$s$       & {\bf 14.48} & 0.13 & 0.78  & 0.65 & 5.51  & 4.71 \\ 
$s^{in}$  & {\bf 14.10} & 0.14 & 2.17  & 1.28 & 17.32 & 6.11 \\ 
$s^{out}$ & {\bf 14.05} & 0.13 & 2.08  & 1.14 & 19.31 & 4.86 \\ \hline
$cc$      & 0.99        & 0.70 & {\bf 83.38} & 4.83 & 2.75  & 1.62 \\ 
$bt$      & {\bf 13.73} & 0.19 & 6.65  & 1.31 & 14.66 & 10.14 \\ \hline
$\lambda$ & 81.80 & 0.83 & 12.53 & 0.09  & 3.24 & 0.62 \\ \hline
  \end{tabular}
  \label{compPCA}
\end{table}

\begin{table}
  \centering
  \caption{Principal components formation with measures of symmetry described (see Section~\ref{measures}). LAU list, $ws=1000$ messages in 20 disjoint positioning was used for statistics. In this case, clusterization is pushed to third components. Second component is primarily symmetry measures, but also out degree and strength, and disequilibrium standard deviation. Betweenness centrality again has a role similar to degree, but weaker. Clusterization component combines with disequilibrium, while asymmetry is combined to out degree and strength. Three components has in average 80.36\% of dispersion.}
  \begin{tabular}{|l|c|c| c|c| c|c|}\hline
 & \multicolumn{2}{c|}{PC1} & \multicolumn{2}{c|}{PC2} & \multicolumn{2}{c|}{PC3}  \\\hline
       & $\mu$ & $\sigma$ & $\mu$ & $\sigma$ & $\mu$ & $\sigma$  \\\hline
$d$            & {\bf 11.51} & 0.42 & 2.00  & 0.76 & 2.39  & 0.49 \\ 
$d^{in}$       & {\bf 11.45} & 0.34 & 2.86  & 0.91 & 1.68  & 0.67 \\
$d^{out}$      & {\bf 10.68} & 0.60 & {\bf 7.43}  & 1.00 & 3.00  & 1.02 \\
$s$            & {\bf 11.37} & 0.42 & 1.75  & 0.71 & 4.31  & 0.63 \\ 
$s^{in}$       & {\bf 11.33} & 0.35 & 2.39  & 1.10 & 3.69  & 0.86 \\ 
$s^{out}$      & {\bf 10.74} & 0.55 & {\bf 6.14}  & 1.05 & 4.75  & 0.98 \\ \hline
$cc$           & 0.91        & 0.64 & 2.68  & 1.67 & {\bf 22.27} & 6.43 \\ 
$bt$           & {\bf 10.87} & 0.38 & 1.17  & 0.93 & 4.03  & 1.42 \\ \hline
$asy$          & 3.99        & 1.45 & {\bf 18.13} & 1.67 & 2.55  & 1.77 \\
$\mu_{asy}$    & 4.15        & 1.40 & {\bf 17.07} & 1.78 & 2.49  & 1.67 \\
$\sigma_{asy}$ & 1.21        & 0.67 & {\bf 17.49} & 0.79 & 3.29  & 2.33 \\
$dis$          & 5.78        & 0.51 & 1.94  & 1.28 & {\bf 24.75} & 3.73 \\
$\mu_{dis}$    & 0.79        & 0.49 & {\bf 14.00} & 1.14 & 3.73  & 3.13 \\
$\sigma_{dis}$ & 5.18        & 0.72 & 4.93  & 2.48 & {\bf 17.04} & 4.78 \\ \hline
$\lambda$      & 51.09       & 1.07 & 20.04 & 1.31 & 9.23  & 6.63 \\ \hline
  \end{tabular}
  \label{compPCA2}
\end{table}

@@

\subsection{Tables for activity along time}\label{tabTime}
\begin{table*}
%\tiny
    \caption{Percentage of activity ($\frac{\text{counted messages}}{\text{total messages}}$) in each hour, 6 hours and 12 hours. Maximum activity rates are in bold. In 1h columns, minimum activity is also bold. The less active period of the day is around 4-6h. Maximum activity is between 10-13h. Afternoon is most active in 6h division of the day. The noon has $\approx \frac{2}{3}$ of 24h activity. }
\begin{center}
    \begin{tabular}{ |l|| c|c|c| c|c|c| c|c|c| c|c|c|}
        \hline
    & \multicolumn{3}{c|}{CPP} & \multicolumn{3}{c|}{MET} & \multicolumn{3}{c|}{LAU} & \multicolumn{3}{c|}{LAD}  \\ \hline
    & 1h   & 6h & 12h &   1h & 6h & 12h &   1h & 6h & 12h &   1h & 6h & 12h \\ \hline\hline
0h  & 3.66 & \multirow{6}{*}{10.67} & \multirow{12}{*}{33.76} & 2.87  & \multirow{6}{*}{7.15} & \multirow{12}{*}{29.33} & 3.58 & \multirow{6}{*}{10.14} &  \multirow{12}{*}{36.88} & 4.00 & \multirow{6}{*}{10.77} & \multirow{12}{*}{33.13} \\
1h  & 2.76 &                        &                         & 1.77  & & &  2.22 & & & 2.52 & & \\
2h  & 1.79 &                        &                         & 1.04  & & & 1.63 & & & 1.79 & & \\
3h  & 1.10 &                        &                         & 0.64  & & & 1.06 & & & 1.06 & & \\
4h  & {\bf 0.68} &                        &                         & 0.47  & & &  0.84 & & & 0.75 & & \\
5h  & 0.69 &                        &                         & {\bf 0.38}  & & & {\bf 0.82} & & & {\bf 0.66} & & \\\cline{3-3}\cline{6-6}\cline{9-9}\cline{12-12}
6h  & 0.83 & \multirow{6}{*}{23.09} &                         & 0.72  & \multirow{6}{*}{22.18} & & 1.17 & \multirow{6}{*}{26.74} & & 0.85 & \multirow{6}{*}{22.36} &  \\
7h  & 1.24 &                        &                         & 1.33  & & & 2.37 & & & 1.56 & & \\
8h  & 2.28 &                        &                         & 2.67  & & & 3.54 & & & 2.96 & & \\
9h  & 4.52 &                        &                         & 4.40  & & & 6.04 & & & 4.68 & & \\
10h & 6.62 &                        &                         & 6.29  & & & {\bf 6.83} & & & 5.93 & & \\
11h & {\bf 7.61} &                        &                         & 6.78  & & & 6.79 & & & 6.40 & & \\\hline
12h & 6.44 & \multirow{6}{*}{\bf 37.63} & \multirow{12}{*}{\bf 66.24} & {\bf 7.33}  & \multirow{6}{*}{\bf 42.22} & \multirow{12}{*}{ \bf 70.66} & 6.11 & \multirow{6}{*}{\bf 35.65} &  \multirow{12}{*}{ \bf 63.12} & {\bf 6.41} & \multirow{6}{*}{\bf 37.25} &  \multirow{12}{*}{\bf 66.87} \\
13h & 6.04 &                        &                         & 7.08  & & & 6.26 & & & 6.12 & & \\
14h & 6.47 &                        &                         & 7.09  & & & 6.38 & & & 6.33 & & \\
15h & 6.10 &                        &                         & 7.14  & & & 5.93 & & & 5.98 & & \\
16h & 6.22 &                        &                         & 6.68  & & & 5.52 & & & 6.40 & & \\
17h & 6.36 &                        &                         & 6.89  & & & 5.46 & & & 6.02 & & \\\cline{3-3}\cline{6-6}\cline{9-9}\cline{12-12}

@@

\begin{table*}
%\tiny
    \caption{Activity along the days of the month. The pattern is to have no clear prevalent period. One might point a slight tendency for the first two weeks to be more active, although this table does not present statistical foundation for such an assumption. For the scope of this study, differences of activity along the month is assumed to be inexistent.}
\begin{center}
    \begin{tabular}{ |l|| c|c|c| c|c|c| c|c|c| c|c|c|}
        \hline
    & \multicolumn{3}{c|}{CPP} & \multicolumn{3}{c|}{MET} & \multicolumn{3}{c|}{LAU} & \multicolumn{3}{c|}{LAD}  \\ \hline
day    & 1 day & 7 days & 14 days &   1 day & 7 days & 14 days &   1 day & 7 days & 14 days &   1 day & 7 days & 14 days \\ \hline\hline
1  & 3.19 & \multirow{7}{*}{23.05} & \multirow{14}{*}{45.63} & 3.01 & \multirow{7}{*}{25.16} & \multirow{14}{*}{48.08} & 3.34 & \multirow{7}{*}{23.06} &  \multirow{14}{*}{47.31} & 3.22 & \multirow{7}{*}{21.96} & \multirow{14}{*}{46.70} \\
2  & 3.07 &                        &                         & 3.38  & & &  3.38 & & & 3.42 & & \\
3  & 3.20 &                        &                         & 3.55  & & & 3.20 & & & 2.87 & & \\
4  & 3.63 &                        &                         & 4.34  & & & 3.52 & & & 2.91 & & \\
5  & 2.85 &                        &                         & 3.93  & & &  2.68 & & & 3.30 & & \\
6  & 3.67 &                        &                         & 3.76  & & & 3.18 & & & 3.52 & & \\
7  & 3.45 &                        &                         & 3.18  & & & 3.77 & & & 2.27 & & \\\cline{3-3}\cline{6-6}\cline{9-9}\cline{12-12}
8  & 3.12 & \multirow{7}{*}{22.57} &                         & 3.36  & \multirow{7}{*}{22.92} & & 3.62 & \multirow{7}{*}{24.25} & & 3.72 & \multirow{7}{*}{24.73} &  \\
9  & 2.57 &                        &                         & 3.44  & & & 3.82 & & & 3.97 & & \\
10  & 2.92 &                        &                         & 3.17  & & & 3.06 & & & 3.77 & & \\
11  & 3.54 &                        &                         & 3.88  & & & 3.11 & & & 3.27 & & \\
12 & 3.23 &                        &                         & 2.94  & & & 3.40 & & & 2.75 & & \\
13 & 3.39 &                        &                         & 3.29  & & & 3.55 & & & 3.34 & & \\
14 & 3.81 &                        &                         & 2.83  & & & 3.69 & & & 3.93 & & \\\hline
15 & 3.35 & \multirow{7}{*}{23.02} & \multirow{14}{*}{46.31} & 2.72  & \multirow{7}{*}{21.87} & \multirow{14}{*}{ 43.56} & 3.23 & \multirow{7}{*}{22.84} &  \multirow{14}{*}{ 44.01 } & 3.37 & \multirow{7}{*}{22.82} &  \multirow{14}{*}{46.00} \\
16 & 3.77 &                        &                         & 2.96  & & & 2.94 & & & 3.37 & & \\
17 & 3.45 &                        &                         & 3.01  & & & 3.02 & & & 2.95 & & \\
18 & 3.47 &                        &                         & 3.39  & & & 3.63 & & & 3.22 & & \\
19 & 2.90 &                        &                         & 3.42  & & & 3.16 & & & 3.59 & & \\
20 & 2.80 &                        &                         & 3.09  & & & 3.25 & & & 3.21 & & \\
21 & 3.29 &                        &                         & 3.27  & & & 3.61 & & & 3.13 & & \\\cline{3-3}\cline{6-6}\cline{9-9}\cline{12-12}
